<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Crossref vignette}
-->

```{r echo=FALSE, eval=FALSE}
knitr::opts_chunk$set(
  comment = "#>", 
  warning = FALSE, 
  message = FALSE,
  cache = TRUE
)
```

## Installation

Install stable version from CRAN

```{r eval=FALSE}
install.packages("rcrossref")
```

Or development version from GitHub

```{r eval=FALSE}
devtools::install_github("ropensci/rcrossref")
```

```{r}
library("rcrossref")
```

## Citation search

Look up a citation using [OpenURL](http://www.crossref.org/openurl/)

```{r}
cr_citation(doi="10.1371/journal.pone.0042793")
```

Or use CrossRef's [DOI Content Negotiation](http://www.crosscite.org/cn/) service, where you can citations back in various formats, including `apa`

```{r}
cr_cn(dois = "10.1371/journal.pone.0112608", format = "text", style = "apa")
```

There are a lot more styles. We include a dataset as a character vector within the package, accessible via the `get_styles()` function, e.g., 

```{r}
get_styles()[1:5]
```

`bibtex`

```{r}
cat(cr_cn(dois = "10.1126/science.169.3946.635", format = "bibtex"))
```

`bibentry`

```{r}
cr_cn(dois = "10.6084/m9.figshare.97218", format = "bibentry")
```

## Citation count

Citation count, using [OpenURL](http://www.crossref.org/openurl/)

```{r}
cr_citation_count(doi="10.1371/journal.pone.0042793")
```

## Search Crossref metadata API

There are two functions that use an older Crossre API at [http://search.labs.crossref.org/dois](http://search.labs.crossref.org/dois): `cr_search()` and `cr_search_free()`. You can of course use them, but the newer Crossref API available through various functions (`cr_agency()`, `cr_fundref()`, `cr_journals()`, `cr_licenses()`, `cr_members()`, `cr_prefixes()`, and `cr_works()`) is more powerful and will recieve more support going forward. The following functions (of the newer set just mentioend) all use the [CrossRef API](https://github.com/CrossRef/rest-api-doc/blob/master/rest_api.md).

### Look up funder information

```{r}
cr_fundref(query="NSF")
```

### Check the DOI minting agency

```{r}
cr_agency(dois = '10.13039/100000001')
```

### Search works (i.e., articles, books, etc.)

```{r}
cr_works(filter=c(has_orcid=TRUE, from_pub_date='2004-04-04'), limit=1)
```

### Search journals 

```{r}
cr_journals(issn=c('1803-2427','2326-4225'))
```

### Search license information

```{r}
cr_licenses(query = 'elsevier')
```

### Search based on DOI prefixes

```{r}
cr_prefixes(prefixes=c('10.1016','10.1371','10.1023','10.4176','10.1093'))
```

### Search CrossRef members

```{r}
cr_members(query='ecology', limit = 5)
```

### Get N random DOIs

`cr_r()` uses the function `cr_works()` internally. 

```{r}
cr_r()
```

You can pass in the number of DOIs you want back (default is 10)

```{r}
cr_r(2)
```

### The older functions and API

Search by author

```{r}
cr_search(query = c("renear", "palmer"), rows = 3, sort = "year")[,-6]
```

Search by DOI

```{r}
cr_search(doi = "10.1890/10-0340.1")[,-6]
```

Free search

```{r}
queries <- c("Piwowar sharing data PLOS one", "Priem Scientometrics 2.0 social web",
  "William Gunn A Crosstalk Between Myeloma Cells",
 "karthik ram Metapopulation dynamics override local limits")
cr_search_free(queries)[,-4]
```

## pmid2doi & doi2pmid

DOIs to PMIDs

```{r}
doi2pmid("10.1016/0006-2944(75)90147-7")
```

You can pass in more than 1 DOI

```{r}
doi2pmid(c("10.1016/0006-2944(75)90147-7","10.1186/gb-2008-9-5-r89"))
```

Optionally simplify result to vector

```{r}
doi2pmid(c("10.1016/0006-2944(75)90147-7","10.1186/gb-2008-9-5-r89"), TRUE)
```

PMIDs to DOIs

```{r}
pmid2doi(18507872)
```

Pass in more than 1 PMID

```{r}
pmid2doi(c(1,2,3))
```

Optionally simplify

```{r}
pmid2doi(18507872, TRUE)
```
