---
title: rcrossref introduction 
author: Scott Chamberlain
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{rcrossref introduction}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

## Installation

Install stable version from CRAN

```{r eval=FALSE}
install.packages("rcrossref")
```

Or development version from GitHub

```{r eval=FALSE}
remotes::install_github("ropensci/rcrossref")
```

```{r}
library("rcrossref")
```

## Citation search

CrossRef's [DOI Content Negotiation](http://citation.crosscite.org/docs.html) service, where you can citations back in various formats, including `apa`

```{r}
cr_cn(dois = "10.1371/journal.pone.0112608", format = "text", style = "apa")
```

There are a lot more styles. We include a dataset as a character vector within the package, accessible via the `get_styles()` function, e.g.,

```{r}
get_styles()[1:5]
```

`bibtex`

```{r}
cat(cr_cn(dois = "10.1126/science.169.3946.635", format = "bibtex"))
```

`bibentry`

```{r}
cr_cn(dois = "10.6084/m9.figshare.97218", format = "bibentry")
```

## Citation count

Citation count, using OpenURL

```{r}
cr_citation_count(doi="10.1371/journal.pone.0042793")
```

## Search Crossref metadata API

The following functions all use the [CrossRef API](https://github.com/CrossRef/rest-api-doc/blob/master/rest_api.md).

### Look up funder information

```{r}
cr_funders(query="NSF")
```

### Check the DOI minting agency

```{r}
cr_agency(dois = '10.13039/100000001')
```

### Search works (i.e., articles, books, etc.)

```{r}
cr_works(filter=c(has_orcid=TRUE, from_pub_date='2004-04-04'), limit=1)
```

### Search journals

```{r}
cr_journals(issn=c('1803-2427','2326-4225'))
```

### Search license information

```{r}
cr_licenses(query = 'elsevier')
```

### Search based on DOI prefixes

```{r}
cr_prefixes(prefixes=c('10.1016','10.1371','10.1023','10.4176','10.1093'))
```

### Search CrossRef members

```{r}
cr_members(query='ecology', limit = 5)
```

### Get N random DOIs

`cr_r()` uses the function `cr_works()` internally.

```{r}
cr_r()
```

You can pass in the number of DOIs you want back (default is 10)

```{r}
cr_r(2)
```

